### 2020-06-04 writeup/intro.tex
intro wip

%\textbf{Setup and Main Results.}
In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
To be precise, we define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d. random noise with mean zero and variance $\sigma^2$.
We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, because of an increased sample size.
The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

>>>>

%\textbf{Setup and Main Results.}
In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
To be precise, we define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d. random noise with mean zero and variance $\sigma^2$.
We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
We consider the bias and variance of the multi-task estimator, and connect them to the three components defined above.
%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
%We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.

Our main result is to develop tight concentration bounds for the bias and variance of the multi-task estimator for two tasks.
Since the sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than the variance of the single-task estimator.
In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the reduced variance that scales only with sample size and covariate shift.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than the bias of the single-task estimator (which is $0$).
Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
Using Lemma \ref{lem_cov_shift_informal}, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$
